Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-13 hpmoon-asoco.tex
Checking in changes

@@

\newenvironment{bluecolor}{\par\color{blue}}{\par}

@@

\begin{abstract}

\begin{bluecolor}

%One of the  most extensively used methods to deal with high-dimensional, multi-objective optimization problems are distributed co-evolutionary algorithms. However, only decomposable problems could strictly be implemented in parallel this way. A new parallel island-model evolutionary algorithm approach, which we call {\em selective operator application}, is used here to deal with un-decomposable problems: instead of sharing parts of individuals, each island, hosted by a single processor, applies the variation operators to a specific subset of the whole individual. This avoids extra steps to recompose the complete individuals from other islands before evaluation.

%In this paper, we intend to demonstrate that automatically setting the size of these  overlapping sections, since it focuses the search between borders of the different search spaces, is able to obtain better  results than using the same size independently of the number of islands. In order to demonstrate that, we  have compared this method to other parallel evolutionary techniques considering different number of islands, chromosome sizes and benchmarks. The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems.

%Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables: the higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands. This opens up a new challenge to be addressed in the future, by experimenting with new ways to calculate the overlapping sizes depending of different factors and parameters.

%%%NEW AND SHORTED
Parallel island-model co-evolutionary algorithms are well-known methods, suitable for dealing with large multi-objective optimization problems. In these algorithms, each island modifies a fragment of the chromosome that encodes a possible solution to the problem. In this paper, we want to demonstrate that automatically setting the size of the overlapping fragments depending on the number of islands obtains better results than using the same size. We  have compared this method to other parallel evolutionary techniques considering a different number of islands, chromosome sizes and benchmarks. The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems. This opens a very promising line to automatically adapt the overlapping sizes in this kind of algorithms.

\end{bluecolor}

@@

% Maybe add a sentence explaining what problems are decomposable and which ones are not. - JJ
\begin{bluecolor}
One of the methods that are most extensively used  to deal with high-dimensional, multi-objective optimization problems (MOPs) are distributed co-evolutionary algorithms \cite{Gong15models}. However, only decomposable problems could strictly be implemented in parallel this way. A new parallel island-model evolutionary algorithm approach \cite{Alba02Parallelism} is used here to deal with un-decomposable problems: instead of sharing parts of individuals, each island, hosted by a single processor, applies the variation operators to a specific subset of the whole individual. This avoids extra steps to recompose the complete individuals from other islands before evaluation. 
\end{bluecolor}

%1. MOP ARE
In MOPs, several
objectives have to be simultaneously optimized
\citep{Mora13paretobased,LIU2017344}. Solving a MOP implies optimizing a function composed of several independent cost functions, one per objective. In
these problems the aim is to obtain a set of solutions that are better
than the rest considering all the objectives; this set is known as
the Pareto Front (PF). The solutions in this set are {\em non-dominated},
which means that there is no other solution that is equal or better
for all objectives. The objective of MOP algorithms is to find as many
solutions equally distributed in the Pareto Front as possible. In order to do that the
exploration of the search space must be very efficient, trying to
cover many possible exploration paths at the same time.

%2 COMPUTATION -> PARALLEL
This aspect of searching for non-dominated solutions, as well as, in
many cases, the size of the search space itself, implies a high demand
of computational time, leading to the proposal of parallel and distributed methods to solve them
\citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress,KAUR2018183,XU2018268},
%3 ONE WAY IS TO USE MOEAS BECAUSE
one of which are evolutionary algorithms (EAs)
\citep{DBLP:series/ncs/EibenS15}. EAs are bio-inspired meta-heuristics
that can be effectively used to find nearly optimal solutions for
optimization problems and are easily parallelizable, since they are
population-based. This means that creating a functionally equivalent parallel
version is as easy as distributing the population in communicating
computing nodes, which are usually called islands. The fact that
they are population-based helps find many solutions that compose the
Pareto front simultaneously.

Usually an EA starts by generating a \emph{population}, that is, a set of random solutions, following a user-defined description. Then, it
evaluates each candidate solution, called \emph{individual}, assigning
it a \emph{fitness} value that describes how good the individual is
solving the target problem. New solutions are then generated by
the application of \emph{operators} that either mutate a single
solution or recombine different existing solutions. After each
iteration, called \emph{generation}, the least fit individuals are
removed, and the process continues until a user-defined stop condition
is met.

EAs were extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
One of the best known and referenced MOEAs
\citep{Dorronsoro13superlinear} is the {\em 
  Non-dominated Sorting Genetic Algorithm} (NSGA-II)
\citep{Deb00NSGAII}. Classical genetic operators are applied to all
the individuals, which are divided into different ranks, based on 
dominance, to be selected for the next generations.

@@

Different approaches have been used to parallelize EAs, as each individual can be considered as an
independent unit \citep{Alba13parallel,Gong15models}. Classic methods, such as the
global parallel EAs (Master-Slave), or the spatially structured
algorithms (Island model or Cellular EAs) have been applied
successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
However, in the case of MOEAs, these
approaches \citep{Luna15Survey} need to deal with the whole solution set, the PF.
 This implies to use different distribution
and sharing mechanisms, as there exists a tradeoff between the speedup
achievable from parallelization and the need to globally recombine the
results to accurately identify the PF
\citep{Branke04Parallelizingcone}. % Is that the case with NSGA? - JJ

Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}, 
meaning that the
MOEAs need to deal with large individuals and spend significant extra
time for crossover, mutation and migration.
Different authors have 
proposed methods to divide the decision space (the chromosome) to
improve the performance and solution quality. In this aspect, the
co-evolution model is a dimension-distributed model where a 
high-dimensional problem is divided into lower dimensional ones
\citep{Gong15models,Tonda12cooperative}, and evolved separately. One
example of the application of this technique was described in
\citep{Kimovski15Parallel}. The method presented in that work involves
different workers that evolve sub-populations created and recombined
by a master process, which performs different recombination
alternatives from the parts returned by worker processes. A high
dimensional problem was used to compare these 
alternatives. In \citep{Dorronsoro13superlinear}, a distributed
co-evolutionary island model was used.  Although in both papers
significant speedups were attained, only a low number of nodes were
employed (8). However, when the number of islands is increased, the division
of each section of the chromosome becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time.

@@

A similar approach used to solve this kind of problems is the {\em
  SeLective operator Application} (SLA) presented in this paper. In this case, each island
deals with the whole chromosome, but only modifies a fragment of it in
the crossover and mutation phase depending on the number of islands,
using the whole chromosome for fitness calculation. This allows to
deal with un-decomposable problems.

In our previous work \citep{Garcia16hpmoon} we used this method in a
preliminary experimental setup, although it is worth mentioning we are
establishing its name and acronym in this paper for the first time.
We show
that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, we showed that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. 
This
motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more extensive parameter evaluation. Besides comparing previous methods in this new experimental setup, in this paper we propose
a new method that automatically sets the size of the overlapped
sections depending on the number of available islands, comparing it with previous versions.

@@

The hypothesis of this paper is that the use of automatically calculated overlapped sections of the
chromosome for the SLA can improve the
quality of the solutions in the same computing time with respect to
the baseline, disjoint and partly overlapped methods. 
The size of the overlapped sections is calculated from  the number of available subpopulations in the multi-objective evolutionary algorithm, and tested in a real computational environment.

In order to demonstrate this claim, our new automatic method has been
compared against different overlapping island schemes: a
baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a
SLA version with disjoint sections and a SLA
fixed-size overlapped version. 
Several benchmark problems and different large number of islands
have been used. Results show that this new technique can improve
different quality indicators in the same amount of time when the
problem size is large.

% There's no mention of the type of the benchmark problems. Insert here some characterization, including whether they are epistatic or not - JJ

Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distributing the decision variables: the higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands. This opens up a new challenge to be addressed in the future, by experimenting with new ways to calculate the overlapping sizes depending on different factors and parameters.

@@

Since the early 2000s distributed and parallel EAs
 have been used mostly to leverage systems such
as clusters or grids \citep{Talbi08Parallel}, since a first-order
approach to EA parallelization is as easy as dividing the population
and add a simple communication mechanism among them. But in the case of
MOEAs, the distribution and parallelization are more difficult than in
single-objective EAs. This is because in different steps of the
algorithm a whole set of dependent solutions, the Pareto Front, should
be managed as a whole, spending time in gathering all individuals from
the different processors or islands.

@@

%This is an improvement over the previous? What is the relationship? FERGU: linked
Other kind of approaches have also been explored. The work by Deb et al. \citep{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs). In that work, the dominance of the solutions was divided into the islands using a coordinate transformation. In that paper, the authors concluded that dividing the search space is a good idea, although achieving this is not trivial. The division of the search space has been explored by other researchers, for example, dividing the population into elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}. For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector. Other authors, such as M{\"a}rtens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.

% Is this really cooperative co-evolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
Many real-world problems require high-dimensionality \cite{Zhang17DECAL,XU2018268}.
Addressing this kind of problems with cooperative co-evolution has
also been studied in several works with approaches closer to the one
presented here. The approach to focus on a portion of the chromosome,
as in our overlapped method, was firstly used in the work by
Dorronsoro et al. \citep{Dorronsoro13superlinear}, obtaining
super-linear performance 
in several instances. Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality. Other authors, such as Cao et al. \cite{CaoZLL17} separate the decision variables into several subpopulations after performing an interdependence analysis, but using a fixed number of processors.

@@

Giving the responsibility of different parts of the search space to
different modules, has also been explored lately by some
researchers. For example, some authors focus on the solution space
modeling the PF by dividing it into different clusters, allowing an
easily parallelizable {\em divide and conquer} approach
\citep{cheng2015adaptive}. 
Even other types of metaheuristics, 
such as the Multi-Objective Ant Colony Optimization (MOACO) \cite{Mora13paretobased}
or Artificial Bee Colony Algorithm \cite{LUO2017235}, 
can rely on island models to divide the search space depending on 
the node to achieve better results.

In our previous work \citep{Garcia16hpmoon} we used some of
the aforementioned ideas to compare two different dMOEAs. The first
one divided the chromosome into $P$ sections,  $P$ being the number of
islands. Every island $p$ only performed the mutation and crossover in
that part ($p_{th}$) of the chromosome (the selective operator application), while the fitness was
calculated using the whole individual. After a certain number of
generations, individuals were migrated randomly to other islands. The
performance metrics were calculated at the end of the run. The second
method, selective operator application with overlapping islands, used the $p_{th-1}$ and
$p_{th+1}$ sections of each chromosome, besides the $p_{th}$
part. During the same amount of time, both methods obtained better
results than a baseline algorithm that dealt with the whole chromosome
in each island for crossover and mutation. We discovered that the
performance using one or another method depends on the number of
sections of the individuals and the number of islands used. This
motivated us to find a new automatic method to select this number of
sections of the chromosome to use, depending on the number of
islands. Besides, previous experiments were performed on a single
processor synchronous island model with a limited number of islands
(8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
been used, and on this occasion, the experiments have been run on a parallel
cluster. 
Therefore, at the same time, we are proposing a new method to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.

@@

\subsection{Proposed methods}
In this paper we analyze several SLA algorithms we have
implemented by using a parallel multi-objective baseline algorithm
as a basis for comparisons. Our proposed methods, using different overlapping schemes, 
are based on NSGA-II, as almost all the previous works discussed
before
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. 
Therefore, we have used a basic distributed NSGA-II algorithm without
overlapping sections as the baseline (B).

@@

As in the baseline (B), an individual is migrated to another random
island after a fixed number of generations. In the new island, this
individual will be considered as one of the others in the island,
crossed and mutated in the same way, depending on the island
identifier (from 1 to $P$). Note that, unlike the other works such as the ones
described by Talbi et al. \citep{Talbi08Parallel}, all the islands deal
with complete chromosomes for fitness calculation, so our approach can
deal with decomposable and no decomposable problems.

@@

\subsubsection{SLA with disjoint islands (D)} 
In this approach, each individual of size $L$ is split into $P$ chunks
of size $L/P$. Every island $p$ only performs crossover and mutation
on the $p_{th}$ part of the individuals. Figure \ref{fig:disjoint}
describes this approach.
%
\begin{figure*}[h!tb]
\centering
\includegraphics[width=12cm]{islandDisjoint.jpg}
\caption{SLA with disjoint islands (D): every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals using genetic operators (crossover and mutation). Also, every island evaluates its own individuals using the complete chromosome. After a given number of generations, it cooperates with the other islands through migration.}
\label{fig:disjoint}
\end{figure*}

@@

\begin{figure*}[h!tb]
\centering
\includegraphics[width=12cm]{islandNoDisjoint.jpg}
\caption{SLA with overlapping islands (O): every island $p$ modifies the  $p+1$,
  $p_{th}$ and $p-1$  components (in grey) of the individuals using genetic operators (crossover and mutation). Also, every island evaluates its own individuals using the complete chromosome. After a given number of generations, it cooperates with the other islands through migration.}
  \label{fig:overlapping}
\end{figure*}

\subsubsection{Automatic SLA with overlapping islands (A)} 
As in the previous method, the sections to address by the operators are overlapped, but
instead of using one extra section on each side of the $p$ section ($p+1$
and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$),
being $c$ a value depending on the number of islands.

>>>>

%\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}

%\corrauth{Pablo Garc\'ia-S\'anchez,
%ETS. Ingenier\'ias en Inform\'atica y Telecomunicaci\'on and CITIC-UGR,
%C/Periodista Daniel Saucedo s/n,
%Universidad de Granada,
%18071, Granada, Spain.}

@@

@@

\begin{abstract}
  % First, state the problem!!!! - JJ Pablo: ok!
%Real-world optimization problems usually require to deal with several objectives.
%Multi-objective optimization methods have gained interest in the last
%years because of the performance they can achieve solving this kind of problems. 
%Many of them usually require a high-dimensional
%decision space, and multi-objective Evolutionary Algorithms have been
%successfully used in the past. Due to the large computational cost
%these algorithms require, different parallelization and distribution
%methods have been proposed, with different parallel and distributed
%computer architectures to cope with them.

  \textcolor{blue}{Real world optimization problems usually have many dimensions and
  several objectives. The high dimensionality requires exceptional
  computing power, and the fact that several dimensions have to be
  searched at the same time add additional difficulty.}
% One of the most extended methods to deal with high-dimensional
% multi-objective optimization problems are the distributed
% co-evolutionary algorithms.
% ----------------- This sentence is meaningless. It should be
% substituted by other stating that co-evolutionary algorithms can
% deal with it for some reason
% Besides, we're no longer saying that they are co-evolutionary in the
% title, but "island-based selective operator application". This
% should go to the abstract too - JJ

%In these methods %which ones? coevolutionary or selective operator
                   %application? - JJ
%  each processor deals only with a part of the decision
%space, that is, the individuals belonging to the same sub-population,
%\textcolor{blue}{which are called {\em islands} in this context}, explore the same subset of decision variables. 
\textcolor{blue}{An approach to cope with these issues is to allocate parts of the decision space to different
processors. Thus, each processor only deals with the individuals of a sub-population (called
island in this context) that explores the part of the decision space allocated to the processor.}

However, only
decomposable problems could strictly be implemented in parallel this
way. \textcolor{blue}{A new approach, which we call {\em selective operator application} is presented here to deal with un-decomposable
problems:} % so we are saying that high-dimensional multi-objective
          % problems are a challenge, but we are presenting a solution
          % for non-decomposable problems. What's what? - JJ
% Still not addressed - JJ
instead of sharing parts
of individuals, each processor applies the variation operators to a
specific subset of the whole individual. % this solves... - JJ
% not addressed - JJ
We have previously proved
that extending the length of these subsets, and therefore, sharing
\textcolor{blue}{some search space between islands, implies an
  improvement in different performance metrics}.
% In this paper, we intend to prove that adapting the size of the
% overlapping section, since it improves *, is able to obtain better
% results than a non-adaptive strategy. In order to prove that, we
% compare - JJ
In this paper, a new method for automatically
adapting the size of the overlapping, or shared, sections of the
individuals has been compared to other collaborative evolutionary
techniques considering different number of islands, chromosome sizes
and benchmarks. The analysis of the obtained experimental results, by
using different metrics, shows that our approach can provide
statistically significant improvements with respect to the base
algorithm \textcolor{blue}{in high-dimensional multi-objective problems}. 
Results also show that the relation between the number of
islands (subpopulations) and the length of the chromosome (number of
decision variables) is also a relevant factor to determine the most
efficient alternative to distribute the decision variables.   % Say
                                % something how it's relevant, and
                                % what you have to do if you have so
                                % many decision variables - JJ
\textcolor{blue}{This opens up a new challenge that to be addressed in the future.}
% This
                                % solves a problem or challenge we
                                % hadn't stated. - JJ Pablo: metido, mira a ver si queda frase memorable

@@

%Introduction should start in the same way as the abstract. And
%starting with something that is not really applicable here, talking
%about general parallel evolutionary algorithms, is even worse.
% Right way (IMNSHO)
% 1. Multiobjective problems are
% 2. They usually require a good amount of computation → parallel
% distributed
% 3. One way to solve them is to use MOEAs _because_ they can be
% easily parallelized
% 4. But the easy paralellization is not necessarily efficient.
% 5. We have proposed the HPMOON (or whatever) technique to improve
% it. In paper (whatever) we proved that (whatever)
% 6. In this paper we will be proving whatever - JJ FERGU: Addressing JJ order
% OK - JJ

%1. MOP ARE
Multi-objective optimization problems (MOP) are those where several
objectives have to be simultaneously optimized
\citep{Mora13paretobased,LIU2017344}. Solving a MOP implies optimizing a function composed of several independent cost functions, one per objective. In
these problems the aim is to obtain a set of solutions that are better
than the rest, considering all the objectives; this set is known as
the Pareto Front (PF). The solutions in this set are {\em non-dominated},
which means that there is no other solution that is equal or better
for all objectives; the objective of MOP algorithms is to find as many
solutions equally distributed in the Pareto Front as possible, and in order to do that the
exploration of the search space must be very efficient, trying to
cover many possible exploration paths at the same time.

%2 COMPUTATION -> PARALLEL
This aspect of searching for non-dominated solutions, as well as, in
many cases, the size of the search space itself, implies a high demand
of computational time, leading to the proposal of parallel and distributed methods to solve them
\citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress,KAUR2018183,XU2018268},
%3 ONE WAY IS TO USE MOEAS BECAUSE
one of which are evolutionary algorithms (EAs)
\citep{DBLP:series/ncs/EibenS15}. EAs are bio-inspired meta-heuristics
that can be effectively used to find nearly optimal solutions for
optimization problems and are easily paralellizable, since they are
population-based and creating a functionally equivalent parallel
version is as easy as distributing the population in communicating
computing nodes, which are usually called islands. The fact that
they are population-based helps find many solutions that compose the
Pareto front simultaneously.

%The availability of metaheuristics which are able to efficiently approach these multi-objective optimization problems have made it possible to cope with many real applications from such multi-objective point of view [4, 5, 6, 7, 8].  Evolutionary algorithms (EAs) [9] are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems and have been extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) [29].

Usually an EA starts by generating a set of random solutions, called
\emph{population}, following a user-defined description. Then, it
evaluates each candidate solution, called \emph{individual}, assigning
it a \emph{fitness} value that describes how good the individual is
with regard to the target problem. New solutions are then generated by
the application of \emph{operators} that either mutate a single
solution or recombine different existing solutions. After each
iteration, called \emph{generation}, the least fit individuals are
removed, and the process continues until a user-defined stop condition
is met.

\textcolor{blue}{EAs have been extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}}.
One of the best known and referenced MOEAs
\citep{Dorronsoro13superlinear} is the {\em 
  Non-dominated Sorting Genetic Algorithm} (NSGA-II)
\citep{Deb00NSGAII}. Classical genetic operators are applied to all
the individuals, which are divided into different ranks, based on the
dominance, to be selected for the next generations.
% This paragraph has nothing to do with anything. Is it useful for
% what you are doing in the paper? Is there any challenge that you
% will be solving here? For instance, you could talk about the problem
% it's got for parallelization and how it deals with them - JJ FERGU: Could you add some paragraph to justify it? (use \textcolor{blue}{} please)

@@

Different approaches have been used to parallelize EAs, as each individual can be considered as an
independent unit \citep{Alba13parallel,Gong15models}. Classic methods, such as the
global parallel EAs (Master-Slave), or the spatially structured
algorithms (Island model or Cellular EAs) have been applied
successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
However, in the case of MOEAs, these
approaches \citep{Luna15Survey} need to deal with the whole solution set, the PF.
 This implies to use different distribution
and sharing mechanisms, as there exist a tradeoff between the speedup
achievable from parallelization and the need to globally recombine the
results to accurately identify the PF
\citep{Branke04Parallelizingcone}. % Is that the case with NSGA? - JJ

\textcolor{blue}{Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}}, % No they don't, and
                                % if they do, add a reference - JJ FERGU: added references
meaning that the
MOEAs need to deal with large individuals and spend significant extra
time for crossover, mutation and migration. %depending on the
                                %language, this time might not be
                                %significant at all, and will depend
                                %on the length of the chromosome, not
                                %the part of the chromosome you will
                                %be applying it to. Besides, this is
                                %not the critical part of the
                                %algorithm, the critical part is
                                %searching the solution space. 
Different authors have % this is only one possibility. You should talk
                       % about simple island models, too - JJ
proposed methods to divide the decision space (the chromosome) to
improve the performance and solution quality. In this aspect, the
co-evolution model is a dimension-distributed model where a % first
                                % reference to co-evolution in this
                                % paper. Is it still a paper about
                                % co-evolution? - JJ
high-dimensional problem is divided into lower dimensional ones
\citep{Gong15models,Tonda12cooperative}, and evolved separately. One
example of application of this technique was described in
\citep{Kimovski15Parallel}. The method presented in that work involves
different workers that evolve sub-populations created and recombined
by a master process, which performs different recombination
alternatives from the parts returned by worker processes. A high
dimensional problem was used to compare these 
alternatives. In \citep{Dorronsoro13superlinear}, a distributed
co-evolutionary island model was used.  Although in both papers
significant speedups were attained, only a low number of nodes were
employed (8). However, when the number of islands is increased, the division
of each section of the chromosome becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time.

@@

A similar approach used to solve this kind of problems is the {\em
  selective operator application} (SLA) \textcolor{blue}{presented in this paper}. In this case, each island
deals with the whole chromosome, but only modifies a fragment of it in
the crossover and mutation phase depending on the number of islands,
using the whole chromosome for fitness calculation. This allows to
deal with un-decomposable problems. % if the whole chromosome is used,
                                % mutation and crossover will take the
                                % same time. You are modifying the
                                % search space, though. 
In our previous work \citep{Garcia16hpmoon} we used this method in a
preliminary experimental setup, although it is worth mentioning we are
establishing its name and acronym in this paper for the first time.
We proved 
that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, we showed that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. %where we couldn't prove that... Or, we
                          %couldn't experiment... - JJ
This
motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more complete parameter setting. Besides comparing previous methods in this new experimental setup, in this paper we propose
a new method that automatically \textcolor{blue}{sets} the size of the overlapped
sections depending on the number of available islands, comparing it with previous versions.

% We have to
                                % emphasize what is actually done. Is
                                % this an addition to the old paper,
                                % or a complete rewrite? - JJ FERGU: rewritten previous paragraph

@@

The hypothesis of this paper is that the use of \textcolor{blue}{automatically} calculated overlapped sections of the
chromosome for the SLA can improve the
quality of the solutions in the same computing time with respect to
the baseline, disjoint and partly overlapped methods. 
\textcolor{blue}{The size of the overlapped sections are calculated from  the number of available subpopulations in the multi-objective evolutionary algorithm, and tested in a real computational environment.}

In order to prove this claim, our new automatic method has been
compared against different overlapping island schemes: a
baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a
SLA version with disjoint sections and a SLA
fixed-size overlapped version. 
Several benchmark problems and different large number of islands
have been used. Results show that this new technique can improve
different quality indicators in the same amount of time when the
problem size is large.

@@

Since the early 2000s distributed and parallel EAs
 have been used mostly to leverage systems such
as clusters or grids \citep{Talbi08Parallel}, since a first-order
approach to EA parallelization is as easy as dividing the population
and add a simple communication mechanism among them. But in the case of
MOEAs, the distribution and parallelization is \textcolor{blue}{more difficult}
single-objective EAs. This is because in different steps of the
algorithm a whole set of dependent solutions, the Pareto Front, should
be managed as a whole, spending time in gathering all individuals from
the different processors or islands.

@@

%This is an improvement over the previous? What is the relationship? FERGU: linked
\textcolor{blue}{Another kind of approaches has also been explored}. The work by Deb et al. \citep{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs). In that work, the dominance of the solutions was divided into the islands using a coordinate transformation. In that paper, the authors concluded that dividing the search space is a good idea, although achieving this is not trivial. The division of the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}. \textcolor{blue}{For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector.} Other authors, such as M{\"a}rtens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.

% Is this really cooperative co-evolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
\textcolor{blue}{Many real-world problems require high-dimensionality \cite{Zhang17DECAL,XU2018268}.
Addressing this kind of problems with cooperative co-evolution has
also been studied in several works with approaches closer to the one
presented here.} The approach to focus on a portion of the chromosome,
as in our overlapped method, was firstly used in the work by
Dorronsoro et al. \citep{Dorronsoro13superlinear}, obtaining
super-linear performance 
in several instances. \textcolor{blue}{Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality. Others authors, such as Cao et al. \cite{CaoZLL17} separate the decision variables into several subpopulations after performing an interdependence analysis, but using a fixed number of processors.}

@@

Giving the responsibility of different parts of the search space to
different modules, has also been explored lately by some
researchers. For example, some authors focus on the solution space
modeling the PF by dividing it in different clusters, allowing an
easily parallelizable {\em divide and conquer} approach
\citep{cheng2015adaptive}. 
\textcolor{blue}{Even other types of metaheuristics, 
such as the Multi-Objective Ant Colony Optimization (MOACO) \cite{Mora13paretobased}
or Artificial Bee Colony Algorithm \cite{LUO2017235}, 
can rely on island models to divide the search space depending on 
the node to achieve better results. }

In our previous work \citep{Garcia16hpmoon} we used some of
the aforementioned ideas to compare two different dMOEAs. The first
one divided the chromosome into $P$ sections, being $P$ the number of
islands. Every island $p$ only performed the mutation and crossover in
that part ($p_{th}$) of the chromosome (the selective operator application), while the fitness was
calculated using the whole individual. After a certain number of
generations, individuals were migrated randomly to other islands. The
performance metrics were calculated at the end of the run. The second
method, selective operator application with overlapping islands, used the $p_{th-1}$ and
$p_{th+1}$ sections of each chromosome, besides the $p_{th}$
part. During the same amount of time both methods obtained better
results than a baseline algorithm that dealt with the whole chromosome
in each island for crossover and mutation. We discovered that the
performance using one or another method depends on the number of
sections of the individuals and the number of islands used. This
motivated us to find a new automatic method to select this number of
sections of the chromosome to use, depending on the number of
islands. Besides, previous experiments were performed on a single
processor synchronous island model with a limited number of islands
(8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
been used, and on this occasion, the experiments have been run on a parallel
cluster. 
\textcolor{blue}{Therefore, at the same time, we are proposing a new method to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.}

@@

\subsection{Proposed methods}
In this paper we analyse several SLA algorithms we have
implemented by using a parallel multi-objective baseline algorithm
as a basis for comparisons. Our proposed methods, using different overlapping schemes, %methods or method?
                                %Which methods? - JJ Fergu: clarifying
are based on NSGA-II, as almost all the previous works discussed
before
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. % This is SoA stuff - JJ FERGU: Yes, I added it here againg because a reviewer wasn't very attentive
Therefore, we have used a basic distributed NSGA-II algorithm without
overlapping sections as the baseline (B).

@@

As in the baseline (B), an individual is migrated to another random
island after a fixed number of generations. In the new island, this
individual will be considered as one of the others in the island,
crossed and mutated in the same way, depending on the island
identifier (from 1 to $P$). \textcolor{blue}{Note that, unlike the other works such as the ones
described by Talbi et al. \citep{Talbi08Parallel}}, all the islands deal
with complete chromosomes for fitness calculation, so our approach can
deal with decomposable and no decomposable problems. %Don't understand what you say
                                %here. What you are saying is that our
                                %approach can't deal with decomposable
                                %problems, actually. - JJ FERGU: you are right, fixed

@@

\subsubsection{SLA with disjoint islands (D)} 
In this approach, each individual of size $L$ is split into $P$ chunks
of size $L/P$. Every island $p$ only performs crossover and mutation
on the $p_{th}$ part of the individuals. Figure \ref{fig:disjoint}
describes this approach.
%
\begin{figure*}[h!tb]
\centering
\includegraphics[width=12cm]{islandDisjoint.jpg}
\caption{SLA with disjoint islands (D): every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals \textcolor{blue}{using genetic operators (crossover and mutation). Also, every island evaluates its own individuals using the complete chromosome. After a given number of generations it cooperates with the other islands through migration.}}
\label{fig:disjoint}
\end{figure*}

@@

\begin{figure*}[h!tb]
\centering
\includegraphics[width=12cm]{islandNoDisjoint.jpg}
\caption{SLA with overlapping islands (O): every island $p$ modifies the  $p+1$,
  $p_{th}$ and $p-1$  components (in grey) of the individuals \textcolor{blue}{using genetic operators (crossover and mutation). Also, every island evaluates its own individuals using the complete chromosome. After a given number of generations it cooperates with the other islands through migration.}}
  \label{fig:overlapping}
\end{figure*}

\subsubsection{\textcolor{blue}{Automatic} SLA with overlapping islands (A)} 
As in the previous method, the sections to address by the operators are overlapped, but
instead of using one extra section on each side of the $p$ section ($p+1$
and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$),
being $c$ a value depending on the number of islands.
% That's not adaptive. It's simply variable - JJ FERGU: it depends on the number of islands. What term do you suggest?
% FERGU: changed to Automatic
As a first
approach to automatically calculate this value, the results shown in
\citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that
work, the overlapped method ($c=1$) obtained better results when the
number of islands were bigger than 8. On the contrary, when the number of
islands is small, no overlapping is necessary. \textcolor{blue}{So, we have used this
knowledge to propose the formula $c=round(0.2*P-1)/2$ to calculate the
extra sections to overlap}. Therefore, when $P=8$ then $c=0$
(equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
on. \textcolor{blue}{Dividing individuals by blocks of equal size, instead a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
Also, as mentioned, this is only a possible formula to reach above described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.  Figure \ref{fig:adaptive} explains the $A$ method, assuming that $c=2$, for example. }
